---
title       : Magic of the Law of Large Numbers.
subtitle    : Visualizing the fact that distribution of average is just a point.
author      : 
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Goal.

During this short presentation I am going to visualize how the Law of Large Numbers (LLN for short) works.  
Namely I am going to demonstrate the fact of convergence of average of random values to single point even when those random values can evaluate to any real number when they are alone.

--- .class #id 

## Simulation of random values.
```{r simulation}
x1 = rexp(1000, rate = 1 / 5)
x2 = apply(matrix(rexp(1000*50, rate = 1 / 5), nrow = 50), MARGIN = 2, FUN = mean)
x3 = apply(matrix(rexp(1000*1000, rate = 1 / 5), nrow = 1000), MARGIN = 2, FUN = mean)
x4 = apply(matrix(rexp(1000*10000, rate = 1 / 5), nrow = 10000), MARGIN = 2, FUN = mean)
mean(x1)
mean(x2)
mean(x4)
```

--- .class #id 

## Visualisation code.
```{r visualisation code, results = FALSE, warning=FALSE, message=FALSE, fig.show='hide'}
suppressMessages(library(ggplot2))
suppressMessages(library(gridExtra))
g1 = ggplot() + geom_histogram(aes(x = x1), binwidth = 0.1) + coord_cartesian(xlim = c(-1, 13))
g2 = ggplot() + geom_histogram(aes(x = x2), binwidth = 0.05) + coord_cartesian(xlim = c(-1, 13))
g3 = ggplot() + geom_histogram(aes(x = x3), binwidth = 0.05) + coord_cartesian(xlim = c(-1, 13))
g4 = ggplot() + geom_histogram(aes(x = x4), binwidth = 0.05) + coord_cartesian(xlim = c(-1, 13))
g = grid.arrange(g1, g2, g3, g4, ncol = 2)
```

--- .class #id

## Plotting.
```{r plotting, echo = FALSE, fig.width=14}
plot(g)
```


